Delocalization of Eigenvectors in Random Matrices

### 2025-03-22 Draft.tex
p3

$$F(H_{ij}^G) =F(0) + \sum_{k=1}^5 \frac{1}{k!} \frac{d^k}{dt^k}\left. F(tH_{ij}^G)\right\vert_{t=0?1}+ \frac{1}{720} \frac{d^6}{dt^6}\left.F(tH_{ij}^G)\right\vert_{t=t_{ij}^G},$$
for another such $t_{ij}^G\in[0, 1]$.
Then, let us take their difference (\textcolor{red}{verify the matrix identity }$\{--\}$:
$$F(H_{ij}) - F(H_{ij}^G) = \sum_{k=1}^5\frac{1}{k!}\sum_{\ell = 0}^k c_{\ell, k} \partial_{H_{ij}}^\ell \partial_{H_{ji}}^{k-\ell} F(0)\left\{H_{ij}^\ell \left(\overline{H}_{ij} \right)^{k-\ell}- \left(H_{ij}^G\right)^\ell \left(\overline{H}_{ij}^G\right)^{k-\ell}\right\}+$$
$$+\frac{1}{720} \left[\left.\frac{d^6}{dt^6}F(tH_{ij})\right\vert_{t=t_{ij}}-\left.\frac{d^6}{dt^6}F(tH_{ij})\right\vert_{t=t_{ij}^G}\right]$$
By the moment matching condition $(8.1)$, we have: $$\mathbb{E}\left\vert F(H_{ij} - F(H_{ij}^G)\right\vert\lesssim \mathbb{E}\left\vert\left.\frac{d^6}{dt^6}F(tH_{ij})\right\vert_{t=t_{ij}}\right\vert+\mathbb{E}\left\vert\left.\frac{d^6}{dt^6}F(tH_{ij})\right\vert_{t=t_{ij}^G}\right\vert$$
Using the formula we found earlier:
$$\mathbb{E}\left\vert\left.\frac{d^6}{dt^6}F(tH_{ij})\right\vert_{t=t_{ij}}\right\vert\lesssim \sum_{k=0}^6 |H_{ij}|^k \left\vert \partial_{H_{ij}}^\ell \partial_{H_{ji}}^{k-\ell} F(tH_{ij}|_{t=t_{ij}} \right\vert$$

>>>>

$$F(H_{ij}^G) =F(0) + \sum_{k=1}^5 \frac{1}{k!} \frac{d^k}{dt^k}\left. F(tH_{ij}^G)\right\vert_{t=0?1}+ \frac{1}{720} \frac{d^6}{dt^6}\left.F(tH_{ij}^G)\right\vert_{t=t_{ij}^G},$$
for another such $t_{ij}^G\in[0, 1]$.
Then, let us take their difference (\textcolor{red}{verify the matrix identity }$\{--\}$:
$$F(H_{ij}) - F(H_{ij}^G) = \sum_{k=1}^5\frac{1}{k!}\sum_{\ell = 0}^k c_{\ell, k} \partial_{H_{ij}}^\ell \partial_{H_{ji}}^{k-\ell} F(0)\left\{H_{ij}^\ell \left(\overline{H}_{ij} \right)^{k-\ell}- \left(H_{ij}^G\right)^\ell \left(\overline{H}_{ij}^G\right)^{k-\ell}\right\}+$$
$$+\frac{1}{720} \left[\left.\frac{d^6}{dt^6}F(tH_{ij})\right\vert_{t=t_{ij}}-\left.\frac{d^6}{dt^6}F(tH_{ij})\right\vert_{t=t_{ij}^G}\right]$$
By the moment matching condition $(8.1)$, we have: $$\mathbb{E}\left\vert F(H_{ij} - F(H_{ij}^G)\right\vert\lesssim \mathbb{E}\left\vert\left.\frac{d^6}{dt^6}F(tH_{ij})\right\vert_{t=t_{ij}}\right\vert+\mathbb{E}\left\vert\left.\frac{d^6}{dt^6}F(tH_{ij})\right\vert_{t=t_{ij}^G}\right\vert$$
Using the formula we found earlier (\textcolor{red}{write out the cancellation by absolute value}):
$$\mathbb{E}\left\vert\left.\frac{d^6}{dt^6}F(tH_{ij})\right\vert_{t=t_{ij}}\right\vert\lesssim \sum_{k=0}^6 |H_{ij}|^k \left\vert \partial_{H_{ij}}^\ell \partial_{H_{ji}}^{k-\ell} F(tH_{ij})|_{t=t_{ij}} \right\vert$$
Let the LHS and RHS be $\mathcal{P}$ and $\mathrm{Q}$, respectively. We want $\mathcal{Q}\leq W^C$ for some $C \lesssim 1$ , s.t. $\mathcal{Q}\prec 1$ (\textcolor{red}{definition? - revisit}). \\

If that were true, then $\exists$ event $\mathcal{A}$, s.t. $\mathcal{Q}\leq W^\epsilon$ on $\mathcal{A}$ with $P(\mathcal{A})\geq 1-W^{-D}$ (\textcolor{red}{workout the details of }$\epsilon$ and $D$- which one is given by the definition and which one do we retrieve?). Then: 
$$\mathcal{P}\lesssim \mathbb{E}|H_{ij}|^6W^\epsilon + \mathbb{E}|H_{ij}|^6 \mathbf{1}\left[{A^C}\right]W^C\lesssim W^{-3+\epsilon} + W^C \left\{\mathbb{E}|H_{ij}|^{12}\right\}^{1/2} \left\{P(A^C)\right\}^{1/2}\lesssim$$

$$\lesssim W^{-3+\epsilon} + W^C W^{-3} W^{-D_0}$$
We can pick $D_0$, s.t. the stochastically dominating term is $W^{-3+\epsilon}$, s.t. we get $\mathcal{P}+\mathcal{P}^G\lesssim W^{-3+\epsilon}$, i.e: $$\left\vert \mathbb{E}\left(F(H_{ij}\right)\right\vert$$
